\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{}

\usepackage{geometry}
\geometry{
a4paper,
top=1cm,
bottom=1cm,
left=1cm,
right=1cm
}


% certification, experience , tools,
  
% \titleformat{\subsection}{\filright\color{subheadings}
% \fontspec{Helvetica}\fontsize{12pt}{12pt}\selectfont\bfseries\uppercase}{}{0em}{}

\begin{document}

%     TITLE NAME

\begin{center}
    \section{}{ 
        \Large\textbf{Jayasai Dodla}

        \href{mailto:jayasaidodla@gmail.com}{jayasaidodla@gmail.com} | +91 9063560031
    }
    \rule{0.95\textwidth}{0.2pt}
\end{center}
%     COLUMN ONE

\begin{minipage}[t]{0.33\textwidth}

    %     EDUCATION

    \section{Education}

    \subsection{RMK Engineering College}
    \descript{Computer Science Engineering}
    % \location{Expected Jun 2025 | CGPA : 8.88 / 10.0 \\Thiruvallur, India}
    \location{Expected Jun 2025 | CGPA : 8.70 }
    \location{Thiruvallur, India}
    \sectionsep

    \subsection{Sri Chaitanya Boys Jr\\ College}
    \descript{Higher Secondary}
    \location{Jul 2021 | Score : 95 \% }
    \location{Krishna, India}
    % \location{Jul 2021 | Score : 95 \% \\Dharmapuri, India}

    \sectionsep

    % \subsection{Senthil Public School CBSE}
    \subsection{Kairali EM High School}
    \descript{High School}
    % \location{May 2019 | Score : 89.6 \% \\Dharmapuri, India}
    \location{May 2019 | Score : 89.6 \%}
    \location{Nellore, India}
    \sectionsep


    %     SKILLS

    \section{Skills}
    \subsection{Programming}
    \location{Confident:}
    C \textbullet{} C++ \textbullet{}  Python \textbullet{} HTML \textbullet{} CSS

    \location{Familiar:}
    Java \textbullet{} Javascript \textbullet{} SQL
    \sectionsep

    \subsection{Tools}
    Github \textbullet{} VSCode

    %     LINKS

    \section{Links}

    \href{https://github.com/gnanaprakash2918}
    Github:// \href{https://github.com/gnanaprakash2918}{\bf gnanaprakash2918} \\

    \href{https://www.linkedin.com/in/gnanaprakash2918/}
    Linkedin://  \href{https://www.linkedin.com/in/gnanaprakash2918/}{\bf gnanaprakash2918} \\

    \href{https://leetcode.com/gnanaprakash2918/}
    Leetcode://  \href{https://leetcode.com/gnanaprakash2918/}{\bf gnanaprakash2918} \\

    \href{https://auth.geeksforgeeks.org/user/gnanaprakash2918}
    GeeksForGeeks://  \href{https://auth.geeksforgeeks.org/user/gnanaprakash2918}{\bf gnanaprakash2918} \\

    \href{https://codeforces.com/profile/gnanaprakash2918}
    Codeforces://  \href{https://codeforces.com/profile/gnanaprakash2918}{\bf gnanaprakash2918} \\

    \sectionsep



    %     COURSEWORK

    \section{Coursework}
    \subsection{UnderGraduate}
    Data Structures and Algorithms \\
    Object Oriented Programming \\
    Operating Systems \\
    Computer Networks \\
    Database Management Systems \\
    \sectionsep

    % {\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst 2x) }}} \\

    % Interests
    \section{Interests}
    Competitive programming \textbullet{} DSA \textbullet{} Linux
    \sectionsep

    \section{Responsibilities}
    \textbullet{} Recognized High Performers Committee Member

    %     COLUMN TWO

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

    % EXPERIENCE

    \section{Experience}

    \runsubsection{Infosys Online Training Program on AI}
    \descript{| Trainee }
    \location{07.08.2023 to 14.08.2023 | Virtual Trainee}
    \vspace{\topsep}
    \begin{tightemize}
        \item Completed a 1-week virtual training on \textbf{``Introduction to AI''} in the SpringBoard Platform.
        \item Gained an introduction to \textbf{Various Domains in AI}.
    \end{tightemize}
    \sectionsep

    \runsubsection{National Small Industries Corporation Limited}
    \descript{| Trainee }
    \location{02.01.2023 to 16.01.2023 | Virtual Trainee}
    \begin{tightemize}
        \item Completed a 2-week virtual training on \textbf{``Industrial-Based Android Application Development Using IoT''}.
        \item Gained an introduction to \textbf{Android Studio} Tools.
    \end{tightemize}
    \sectionsep

    % \runsubsection{Google}
    % \descript{| Open Source Contributor \& Team Leader}
    % \location{May 2013 – Aug 2013 | Mountain View, CA}
    % \begin{tightemize}
    %     \item Worked on the YouTube Captions team, in Javascript and Python to plan, to design and develop the full stack to add and edit Automatic Speech Recognition captions. In production.
    %     \item Created a backbone.js-like framework for the Captions editor.
    % \end{tightemize}
    % \sectionsep

    %     RESEARCH


    \section{Projects}
    % Recent ones first

    % \runsubsection{Stock Price Prediction}

    % \location{Python | \href{}{\textbf{GitHub Link}}}
    % \begin{tightemize}
    %     \item Developed a predictive modeling project utilizing \textbf{LSTM} neural networks to forecast stock prices.
    %     \item Leveraged TensorFlow to train the model with historical stock price data obtained from Google.
    % \end{tightemize}
    % \sectionsep


    \runsubsection{Reddit Posts Scraper}

    \location{Python | PRAW API | \href{https://github.com/gnanaprakash2918/Reddit-Scraper}{\textbf{GitHub Link}}}
    % \vspace{\topsep}
    \begin{tightemize}
        \item Developed a Reddit Scraper, which lets users scrape reddit posts and comments.
        \item Enables Users to Scrape Posts by Month, Post and URL of a subreddit.
        \item Utilized \textbf{Python Reddit API Wrapper API} from reddit to scrape the data from reddit.
    \end{tightemize}
    \sectionsep

    \runsubsection{File Organizer}

    \location{C++ | \href{}{\textbf{GitHub Link}}}
    \begin{tightemize}
        \item Developed a C++ Script that classifies files into different directories based on their extension.
        \item Implemented the Script using {\textbf{std::filesystem}} in C++ Standard Library to facilitate organization of files into designated directories.
    \end{tightemize}
    \sectionsep



    % \runsubsection{Cornell Phonetics Lab}
    % \descript{| Head Undergraduate Researcher}
    % \location{Mar 2012 – May 2013 | Ithaca, NY}
    % Led the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research.
    % \sectionsep

    % Courses and certifications
    \section{Awards and Certifications}

    \runsubsection{Glance Village Hackathon RMKEC \textbf{(2023)}}

    \location{\textbf{Barren Land Detection and Fertilizer Recommendation}}
    \begin{tightemize}
        \item Secured \textbf{1\textsuperscript{st}} prize in a competition of around \textbf{200+} teams.
        \item Collaborated in a team of 6 members, specializing in identifying barren lands using \textbf{Google Earth Engine}.
        \item Proposed ideas which played a key role in securing the first prize in a competition.
    \end{tightemize}
    \sectionsep

    \runsubsection{College Premier League Contest Skillrack \textbf{(2022)}}

    \location{\textbf{Skillrack Gold Medalist}}
    \begin{tightemize}
        \item Participated in the College Premier League organized by Skillrack, involving \textbf{365} students from colleges across Tamil Nadu.
        \item Solved all 3 assigned problems, earning a gold medal on the platform.
    \end{tightemize}
    \sectionsep

    \runsubsection{The Joy of Computing using Python \textbf{(2022)}}

    \location{\textbf{NPTEL Certification}}
    \begin{tightemize}
        \item Completed a 12-week course titled ``Joy of Computing Using Python''.
        \item Achieved a consolidated score of \textbf{84\%} in the final examination.
    \end{tightemize}
    \sectionsep

    \runsubsection{IntraDepartment Paper Presentation \textbf{(2022)}}

    \location{\textbf{Cancer Detection using Machine Learning}}
    \begin{tightemize}
        \item Presented a Paper on diagnosis of cancer utilizing {\textbf{MRI} and \textbf{CT} scans}.
        \item Explored possible advancements in cancer detection.
    \end{tightemize}
    \sectionsep



    %     AWARDS

    % \section{Awards}
    % \begin{tabular}{rll}
    %     2023 & 1\textsuperscript{st}/500+ Teams & Glance Village Hackathon RMKEC                                                                                    \\
    %     2022 & 1\textsuperscript{st}/365        & \href{http://www.skillrack.com/profile/354901/b53dfbae463b744bd0c3ad6c8c78658025d49aec} {Skillrack} Gold Medalist \\
    % \end{tabular}
    % \sectionsep


    %     PUBLICATIONS
    % \section{Publications}
    % \renewcommand\refname{\vskip -1.5em}
    % \bibliographystyle{abbrv}
    % \bibliography{publications}
    % \nocite{*}

\end{minipage}
\end{document}  \documentclass[]{article}
